FLM for growth as function of SPEI

### 2021-01-08 analysis/paper/vital rate models.Rmd
moved joining of demographic and spei datasets to wrangling script.

```{r data, echo=TRUE}
xa <- read_rds(here("analysis", "data", "derived_data", "xa_spei_lags.rds"))
demog <- read_rds(here("analysis", "data", "derived_data", "ha_survey.rds"))
plot_coords <- read_csv(here("analysis", "data", "raw_data", "plot_coords.csv"))
```

```{r}
length(unique(demog$ha_id_number))
range(demog$year)
2009-1998
```

# Join data sets

## Prep precip data
Get only rows for february (the month of the census), and year for joining

```{r}
xa2 <- 
  xa %>%
  filter(month(yearmonth) == 2) %>% 
  mutate(year = year(yearmonth), .after =yearmonth) %>% 
  separate(latlon, into = c("lat", "lon"), sep = "_")
xa2
```

Figure out which sites correspond to which grid cells.  The `xa` lat lon are the centers of grid cells that are 0.25º^2

```{r}
unique(xa2$lat)
mean(c(-2.25, -2.5))
```
So, from -2.25 to -2.5

```{r}
unique(xa2$lon)
mean(c(-59.5, -59.75))
mean(c(-59.75, -60)) # Florestal-CF, 5752, 5751, 5750, 5756, CaboFrio-CF
mean(c(-60, -60.25)) # 2206, 2108, 2107, Dimona-CF, 5753, PortoAlegre-CF
```

```{r}
plot_coords
```

```{r}
demog2 <-
  demog %>% 
  mutate(lon = case_when(
    plot %in% c("Florestal-CF", "5752", "5751", "5750", "5756", "CaboFrio-CF") ~ "-59.875",
    plot %in% c("2206", "2108", "2107", "Dimona-CF", "5753", "PortoAlegre-CF") ~ "-60.125",
    TRUE ~ NA_character_
  ), .before = plot)
demog_full <- 
  full_join(demog2, xa2, by = c("lon", "year")) %>% 
  select(-lon, -lat, -yearmonth)
```

>>>>

```{r data, echo=TRUE}
demog_full <-
  read_csv(here("analysis", "data", "derived_data", "ha_demog_spei.csv"), 
           col_names = TRUE,
           cols(plot = col_character(),
                bdffp_reserve_no = col_character()))
```
